\documentclass{article}

\begin{document}

\section{Abstract}

K3 is a famous Flemish music group.
Recetly they have chnaged their formation.
Rumors claim that the new formation is worse
than the old one.
Here, we investigate if that claim is true,
based on the reviews of their music before
and after the new formation.
We find that the new formation is 
[worse/equal/better].

\section{Introduction}
Hello.

\section{Hypotheses}

Hypothesis: ratings (as a value from 
1 to 10, where 1 is worst and 10 is best)
given to the songs given 
to the previous formation are as high 
as ratings given to the songs given to the
current formation.

\section{Methods}

\paragraph{Data set}
We obtain ratings (which are values from
1 to 10, where 1 is worst and 10 is best)
from a website in which two people 
have rated K3 songs.

\paragraph{Statistical test}
We do not the assume that the
ratings (which are values from 
1 to 10, where 1 is worst and 10 is best)
follows a normal distribution. Due to this,
we use a Mann-Whitney U test to test if
the distributions are the same.

\paragraph{Rejection or acception of hypothesis}
We will be using a value of alpha of 0.05,
because there has not been done any previous
research.

If the p value is below the alpha value,
the hypothesis is accepted, making us conclude
that the groups are equally enjoyable.
Else, we will reject the null hypothesis
and conclude the groups differ in enjoyability.

\section{Results}

We get a p-value of ? from our 
Mann-Whitney U. 

The ratings for the two groups are plotted in
figure 1. 

FIGURE HERE

\section{Conclusion}
From our p-value we conclude that 
the groups are [equally/differently] enjoyable.

[If there is a difference, then:]
We observe in figure 1 that the [first/second] 
group is more enjoyable.

\section{Discussion}

We obtained the data from the reviews done
by only two people. This may result in
a bias. 
Additionally, only one person reviewed
songs of both formations and not all
songs have been reviewed.
Because it is the only data
set available, there was no other option.

\end{document}
